---
title: "Project 2"
author: "Anna Su, Donovan Calvert, Naren Makkapati"
resource_files:
- .Renviron
output:
  html_notebook:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
runtime: shiny
---
This is an R Interactive Document, which uses the [R Markdown](http://rmarkdown.rstudio.com/authoring_basics.html) language to generate HTML. For a brief introduction to R Markdown, please review this [video](https://www.youtube.com/watch?v=DNS7i2m4sB0&feature=youtu.be).

#Load Packages
This [code chunk](http://rmarkdown.rstudio.com/authoring_rcodechunks.html) loads the packages required to run the R code in the document.
The last line of this code chunk enables document caching, which is expalined at this [link](http://rmarkdown.rstudio.com/authoring_rcodechunks.html).

```{r setup, echo=FALSE}
library(tidyverse)
library(shiny)
library(grid)
library(data.world)
library(DT)
library(shinydashboard)
library(plotly)
library(lubridate)
knitr::opts_chunk$set(echo = TRUE)
```

#Display Session Information
The [sessionInfo() fuction](https://cran.r-project.org/web/packages/sessioninfo/sessioninfo.pdf) queries and prints information about the current R session including  information about packages, and from where they were installed.
```{r}
sessionInfo()
```

#Section for Links
Data.world Project Link: https://data.world/yuchan-su/s18-edv-project-2

GitHub Classroom Repository link: https://github.com/CannataUTDV/s18dvproject1-su-makkapati-calvert

#Create Dataframes
The sourced code below contains Shiny [eventReactive](https://shiny.rstudio.com/reference/shiny/1.0.1/observeEvent.html) code and queries for the SuperStore database at data.world. The data is saved in variables as functions that return an R dataframe. These are examples data.world parameterized queries; details for data.world queries can be found at this [link](https://cran.r-project.org/web/packages/data.world/vignettes/query.html). The "?"s in the query are parameters. The parameters are filled in (in order) by the paramQuery$params statement.

```{r}
#since you have two different dataframe...load into source here
source("DataA.R", local = TRUE)
source("DataB.R", local = TRUE)
```

#Retrieve Regions from the IBM Attrition dataset
The following query retrieves the distinct region names from the SuperStore dataset at data.world and saves the region names in the regions variable.
```{r}
project <- "https://data.world/cannata/tophatsuperstore" 
data.world::set_config(cfg_env("DW_API")) 

#query that selects region
regions <- data.world::query(data.world::qry_sql(
 "   
	select distinct region
	from superstore 
 "), 
dataset = project)
```
#Create a Regions Variable
Create a Regions variable with a string constructed from the selected regions in the input$selectRegion_1 variable.This Regions variable will be used in the title of the ggplot below.

```{r}
Regions <- eventReactive(c(input$selectRegion_1), { 
  library('stringr')
  str_c(input$selectRegion_1, collapse=', ')
})
```

#Create Panel with Select List
The following code creates an input panel for the Interactive Document, which has a [select box](https://shiny.rstudio.com/reference/shiny/latest/selectInput.html) for selecting regions (notice - choices is set to the regions variable that was loaded by the previous query) For a complete list of Shiny functions, please see this [link](https://shiny.rstudio.com/reference/shiny/latest/).

```{r}
#what panel is this?? The regionselectpanel. So it's the oen taht appears To have all the select TABS. In a way this is a way for people on the website to REDO the query

inputPanel(
  selectInput("selectRegion_1", label = "Select Region",choices = regions, multiple=TRUE, selected=c("East", "West", "Central", "South"))
)
```

#Render and Display the Shipping Costs Histograms

Using [ggplotly](https://www.rdocumentation.org/packages/plotly/versions/4.7.1/topics/ggplotly) and [shinydashborad](https://rstudio.github.io/shinydashboard/structure.html#dynamic-content-1)

```{r}
#show they have four different side 
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Shipping Costs Histogram", tabName = "histogram", icon = icon("dashboard")),
      menuItem("Shipping Costs Density Plot", tabName = "density", icon = icon("dashboard")),
      menuItem("Shipping Costs Histogram and Density Plot", tabName = "both", icon = icon("dashboard")),
      menuItem("Sales Histogram", tabName = "newplot", icon = icon("dashboard")),
      menuItem("Sales Histogram", tabName = "newnewplot", icon = icon("dashboard"))
    )
  ),
  dashboardBody(
    tabItems(
      # 1. "Shipping Costs Histogram" tab content
      tabItem(tabName = "histogram",
        p("You can actually put some descriptive text here - see https://shiny.rstudio.com/articles/css.html"),
        source("Histogram1UI.R",local = TRUE)$value
      ),
      # 2. "Shipping Costs Density Plot" tab content
      tabItem(tabName = "density",
        p("And here."),
        source("Density1UI.R",local = TRUE)$value
      ),
      # 3. "Shipping Costs Histogram and Density Plot" tab content
      tabItem(tabName = "both",
        p("And even here."),
        source("Both1UI.R",local = TRUE)$value
      ),
      # 4. "Sales Histogram" tab content
      tabItem(tabName = "newplot",
        p("And even here."),
        source("NewPlot1UI.R",local = TRUE)$value
      ),
      #creating a differ one, tabname is to be unique in this case; then now you ahve ability to have FIVE plots. And then you go and make the server and UI file to change the graphs
      # 5. "Sales Histogram" tab content
      tabItem(tabName = "newnewplot",
        p("And even here."),
        source("NewPlot1UI.R",local = TRUE)$value
      )
    )
  )
)
source("Histogram1Server.R", local = TRUE)
source("Density1Server.R", local = TRUE)
source("Both1Server.R", local = TRUE)
source("NewPlot1Server.R", local = TRUE)
```

#Naren's Test Code
This is a test by Naren. If you see this, it worked.


#Appendix
Data cleaning Code.


